\TODO{What's the title?}

### 2018-09-18 doc/Paper.tex
Update PDF to daf8d2c4d984da3ed6239fe13805c50e32749742

@@

  We now move on to embed this attribute grammar into Haskell. Semantic rules
  simply become functions, which, given a zipper, return values of the
  attributes. For example,
\begin{hscode}\SaveRestoreHook
~~localMin~::~{\itshape {\itshape Lib}.Zipper}~{\itshape Cxt}~{\itshape Attributes}~({\itshape Tree}~{\itshape Int})~\WithMath{->}{\rightarrow}~{\itshape Int}
\\
\texfamily ~~localMin~z@({\itshape {\itshape Lib}.Zipper}~hole)~=~{\bfseries case}~whereami~hole~{\bfseries of}
\\
\texfamily ~~~~{\itshape C\char95 Leaf}~\WithMath{->}{\rightarrow}~{\bfseries let}~({\itshape Leaf}~x)~=~hole~{\bfseries in}~x
\\
\texfamily ~~~~{\itshape C\char95 Fork}~\WithMath{->}{\rightarrow}~min~(localMin~\$~{\itshape Lib}.unsafeChild~0~z)
\\
\texfamily ~~~~~~~~~~~~~~~~~~(localMin~\$~{\itshape Lib}.unsafeChild~1~z)
\ColumnHook
\end{hscode}\resethooks

>>>>

% Tree positions

@@

  We now move on to embed this attribute grammar into Haskell. Semantic rules
  simply become functions, which, given a zipper, return values of the
  attributes. For example,
\begin{hscode}\SaveRestoreHook
~~localMin~::~{\itshape Zipper}~({\itshape WhereAmI}~{\itshape Position})~({\itshape Tree}~{\itshape Int})~\WithMath{->}{\rightarrow}~{\itshape Int}
\\
\texfamily ~~localMin~z@({\itshape Zipper}~hole~\char95 )~=~{\bfseries case}~whereami~hole~{\bfseries of}
\\
\texfamily ~~~~\parbox{\widthof{CLeaf}}{\textit{C}$_\text{\textit{Leaf}}$}~\WithMath{->}{\rightarrow}~{\bfseries let}~{\itshape Leaf}~x~=~hole~{\bfseries in}~x
\\
\texfamily ~~~~\parbox{\widthof{CFork}}{\textit{C}$_\text{\textit{Fork}}$}~\WithMath{->}{\rightarrow}~{\bfseries let}~{\itshape Just}~l~=~child~0~z;~{\itshape Just}~r~=~child~1~z
\\
\texfamily ~~~~~~~~~~~~~~{\bfseries in}~min~(localMin~l)~(localMin~r)
\ColumnHook
\end{hscode}\resethooks

  Apart from the type signature, the code is pretty straightforward and closely
  mirrors the AG we defined earlier. \text{\texfamily whereami} function allows us to ``look
  around'' and returns the position of the zipper. Thus the \text{\texfamily {\bfseries case}} corresponds
  to the pattern matches on the left of the vertical bars on
  figure~\ref{fig:repmin-AG}.

  Position of the zipper is encoded using the following GADT which can be
  generated automatically using Template Haskell:
\begin{hscode}\SaveRestoreHook
~~{\bfseries data}~{\itshape Position}~::~{\itshape Type}~\WithMath{->}{\rightarrow}~{\itshape Type}~{\bfseries where}
\\
\texfamily ~~~~\parbox{\widthof{CLeaf}}{\textit{C}$_\text{\textit{Leaf}}$}~::~{\itshape Position}~({\itshape Tree}~{\itshape Int})
\\
\texfamily ~~~~\parbox{\widthof{CFork}}{\textit{C}$_\text{\textit{Fork}}$}~::~{\itshape Position}~({\itshape Tree}~{\itshape Int})
\ColumnHook
\end{hscode}\resethooks
  Parametrization on the type of the hole allows the code like
  \text{\texfamily {\bfseries let}\Sp {\itshape Leaf}\Sp x\Sp =\Sp hole\Sp {\bfseries in}\Sp x} to typecheck even though the generic zipper itself knows close
  to nothing about the type of the hole.
